Group B Analysis - Calibration

### 2024-10-24 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
A bunch of edits through Experiment 2

jh.E1_model1_tab.min = broom.mixed::tidy(jh.E1_model1.min) 
jh.E1_model1_obj.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model1_verb.min = jh.E1_model1_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model1_obj_verb.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-noun fixations 
In line with the previous analyses of the remote data, we asked whether participants looked more to the target than to the distractor object during the predictive time window, depending upon the verb condition. The first model constrained the predictive window to the time before the onset of the target noun. We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and scenes (with no covariance between random effects because the model cannot converge with full covariance matrix). Unlike the remote sample, there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (_b_ = `r jh.E1_model1_obj.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj.min %>% pull(p.value) %>% round(digits = 2)`). Also unlike the remote sample, the critical interaction was not in the expected direction, although it was also not statistically significant (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model2_tab.min = broom.mixed::tidy(jh.E1_model2.min) 
jh.E1_model2_obj.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model2_verb.min = jh.E1_model2_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model2_obj_verb.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we did the same, we again saw that the critical interaction is not significant nor in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model3_tab.min = broom.mixed::tidy(jh.E1_model3.min) 
jh.E1_model3_verb.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model3_dur.min = jh.E1_model3_tab.min %>% filter(term == "dur_verb_ms_c")
jh.E1_model3_intxn.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting:dur_verb_ms_c")
```
#### First target fixations after verb
Finally, we addressed whether participants looked to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. On average, participants looked to the target `r jh.our_table1_min$Eat[4]` ms after the noun onset in the restrictive condition and `r jh.our_table1_min$Move[4]` ms after the noun onset in the non-restrictive condition. As in the remote sample, the latencies are overall slower than in results published by Altmann & Kamide (1999) and James et al. (2023). Unlike in the remote sample, however, the difference is in the unexpected direction, such that participants looked to the target faster in the non-restrictive condition.

We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`). Effects of verb duration and its interaction with condition were also not statistically significant (duration: _b_ = `r jh.E1_model3_dur.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_dur.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_dur.min %>% pull(p.value) %>% round(digits = 2)`; interaction: _b_ = `r jh.E1_model3_intxn.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_intxn.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_intxn.min %>% pull(p.value) %>% round(digits = 2)` )

@@

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```
```{r E1b-calib-effect, fig.cap='Calibration scores plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
#I picked this one because it's the same as in E1a
ggplot(jh.cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

### Calibration
As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%. 
Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`. Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.

@@

```
#### Re-analysis After Exclusions
Again, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh`%, which eliminated `r length(bad.subjects.validation.aggro.jh)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.

Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

>>>>

jh.E1_model1_tab.min = broom.mixed::tidy(jh.E1_model1.min) 
jh.E1_model1_obj.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model1_verb.min = jh.E1_model1_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model1_obj_verb.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-noun fixations 
We ran the analysis exactly as before. Unlike with the remote sample, this time there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (_b_ = `r jh.E1_model1_obj.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj.min %>% pull(p.value) %>% round(digits = 2)`). However, the critical interaction was again not statistically significant and indeed in the wrong direction (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model2_tab.min = broom.mixed::tidy(jh.E1_model2.min) 
jh.E1_model2_obj.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model2_verb.min = jh.E1_model2_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model2_obj_verb.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
When we repeated this analysis, the critical interaction was again not significant, nor was it even in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model3_tab.min = broom.mixed::tidy(jh.E1_model3.min) 
jh.E1_model3_verb.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model3_dur.min = jh.E1_model3_tab.min %>% filter(term == "dur_verb_ms_c")
jh.E1_model3_intxn.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting:dur_verb_ms_c")
```
#### First target fixations after verb
On average, participants looked to the target `r jh.our_table1_min$Eat[4]` ms after the noun onset in the restrictive condition and `r jh.our_table1_min$Move[4]` ms after the noun onset in the non-restrictive condition. As in the remote sample, the latencies are overall slower than in results published by Altmann & Kamide (1999) and James et al. (2023). Unlike in the remote sample, however, the difference is in the unexpected direction, such that participants looked to the target faster in the non-restrictive condition. In any case, no effects were significant; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`). Effects of verb duration and its interaction with condition were also not statistically significant (duration: _b_ = `r jh.E1_model3_dur.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_dur.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_dur.min %>% pull(p.value) %>% round(digits = 2)`; interaction: _b_ = `r jh.E1_model3_intxn.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_intxn.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_intxn.min %>% pull(p.value) %>% round(digits = 2)` )

@@

#correlate
jh.m3_diff_cor <- cor.test(jh.cali.analy.3$diff, jh.cali.analy.3$M, use = "pairwise.complete.obs")
#0.04122796
jh.m3_diff_cor_r <- jh.m3_diff_cor$estimate
jh.m3_diff_cor_p <- jh.m3_diff_cor$p.value
```
```{r E1b-calib-effect, fig.cap='Calibration scores in Exp. 1b, plotted against the verb effect, operationalized as the latency of the first target fixation in the non-restricting verb condition minus that in the restricting verb condition.'}
#I picked this one because it's the same as in E1a
ggplot(jh.cali.analy.3, aes(x=M, y=diff))+
  geom_point()+
  geom_smooth(method="lm", formula = y ~ x)+
  labs(x="Calibration Score", y="Verb Effect (ms)")+
  theme_bw()+
  theme(panel.grid.minor = element_blank())

@@

### Calibration
As before, participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point. Calibration quality ranged from `r min(jh.validation.percent$M) %>% round(digits = 2)`% to `r max(jh.validation.percent$M) %>% round(digits = 2)`%. 
As in Exp. 1a, calibration quality was not significantly correlated with any of the three effects (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`. Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.

@@

```
#### Re-analysis After Exclusions
Again, we re-analyzed the data focusing on participants with validation accuracy of at least `r validation.threshold.aggro.jh`% (N = `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))`). Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

### 2024-10-24 group-a/E1-analysis-replication.Rmd
A bunch of edits through Experiment 2

E1_model1_tab.min = broom.mixed::tidy(E1_model1.min) 
E1_model1_obj.min = E1_model1_tab.min %>% filter(term == "object_classtarget.object")
E1_model1_verb.min = E1_model1_tab.min %>% filter(term == "verb_typerestricting")
E1_model1_obj_verb.min = E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-noun fixations
In our first two analyses, we asked whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting. The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun. We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix)^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`. There were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

E1_model2_tab.min = broom.mixed::tidy(E1_model2.min) 
E1_model2_obj.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object")
E1_model2_verb.min = E1_model2_tab.min %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
Altmann and Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we did the same^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`, we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

#### First target fixations after verb
Finally, we addressed whether participants looked to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language]. Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.

We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`. There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

We tested whether a participant's calibration quality was correlated with their effect size. There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions). Across the three effects of interest, calibration quality was not significantly correlated (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`. Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3. The figure makes clear that there is a large proportion of participants with calibration scores under 50%.

#### Re-analysis After Exclusions
We re-analyzed the data after excluding participants with calibration scores under 50% (N = `r n.bad.subjects.validation.aggro`). The following analyses thus included `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants.

We tested the same three models under these more aggressive exclusion criteria. The first two models, comparing target and distractor fixations in the predictive window, produced very similar results; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`). However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded a statistically significant result, unlike in the previous set of analyses with all participants included (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).

>>>>

E1_model1_tab.min = broom.mixed::tidy(E1_model1.min) 
E1_model1_obj.min = E1_model1_tab.min %>% filter(term == "object_classtarget.object")
E1_model1_verb.min = E1_model1_tab.min %>% filter(term == "verb_typerestricting")
E1_model1_obj_verb.min = E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-noun fixations
In our first two analyses, we attempted to replicate the original finding that participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting. The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun. We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix).^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`] This is analogous to the F1/F2 analyses used in the original but is more commonly used now. Contrary to the original study, there were no significant effects, although the critical interaction was in the expected direction (_b_ = `r E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

E1_model2_tab.min = broom.mixed::tidy(E1_model2.min) 
E1_model2_obj.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object")
E1_model2_verb.min = E1_model2_tab.min %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.min = E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
In a follow-up analysis, Altmann and Kamide aligning the predictive time window with the offset of the verb rather than the onset of the noun as above, finding the same result: participants looked significantly more to the target than to the distractor. When we repeated this analysis,^[ `lme4` syntax: `lmer_alt(probability ~ object_type*verb_condition + (object_type*verb_condition || subject) + (object_type*verb_condition || scene)`] we again saw that the critical interaction is not significant but numerically in the expected direction (_b_ = `r E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

#### First target fixations after verb
Finally, we addressed whether participants looked to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. On average, participants looked to the target `r E1_latency_table_min$Eat.x[2]` ms after the noun onset in the restrictive condition [compared to `r E1_latency_table_min$Eat.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[2]` in @james2023language;] and `r E1_latency_table_min$Move.x[2]` ms after the noun onset in the non-restrictive condition [compared to `r E1_latency_table_min$Move.y[2]` in @altmannIncrementalInterpretationVerbs1999 and `r first.fix.avg.JMW$Noun.on[1]` in @james2023language;]. Thus, first fixations were not only delayed relative to those in the previous studies compared here, but also showed a smaller difference between conditions.

Critically, we failed to replicate the difference between conditions: participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).^[ `lme4` syntax: `lmer_alt(time ~ verb_condition*verb_duration + (verb_condition || subject) + (verb_condition || scene)`]

@@

We tested whether a participant's calibration quality was correlated with their effect size. There were three effects of interest: the verb-by-object interaction in predicting fixation probabilities, both in the (1) pre-noun-onset and (2) pre-verb-offset windows (calculated as the difference in target-over-distractor preference between verb conditions), and (3) the effect of verb on the timing of the first target fixation (calculated as the difference in target latency between verb conditions). Calibration quality was not significantly correlated with any of the free effects (Effect 1: Pearson's _r_ = `r m1_diffdiff_cor_r`, _p_ = `r m1_diffdiff_cor_p`, Effect 2: Pearson's _r_ = `r m2_diffdiff_cor_r`, _p_ = `r m2_diffdiff_cor_p`, Effect 3: Pearson's _r_ = `r m3_diff_cor_r`, _p_ = `r m3_diff_cor_p`. Figure\ \@ref(fig:E1-calib-effect) plots the relation between calibration scores and Effect 3.

#### Re-analysis After Exclusions
The figure makes clear that there is a large proportion of participants with calibration scores under 50%. Thus, we re-analyzed the data with the `r nlevels(droplevels(critical.trials.filtered.aggro$subject_id))` participants who had calibration scores of at least 50%. The first two models, comparing target and distractor fixations in the predictive window, produced very similar results as before; the critical interaction  was not statistically significant (Pre-noun-onset window: _b_ = `r E1_model1_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window: _b_ = `r E1_model2_obj_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro %>% pull(p.value) %>% round(digits = 2)`). However, the final model, which tested the effect of verb condition on the timing of fixations to the target, yielded the expected statistically significant result (_b_ = `r E1_model3_verb.aggro %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro %>% pull(p.value) %>% round(digits = 2)`).

### 2024-10-24 group-b/E2-analysis-calibration.Rmd
A bunch of edits through Experiment 2

```
#### Re-analysis After Exclusions
There were `r e2.n.bad.subjects.aggro` participants whose calibration score was under 50%. When those participants were removed from the analyses, critical results were in line with the main analyses: there remains a clear gaze bias in the free-viewing condition (first: _b_ =  `r E2_gaze_model.aggro_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model.aggro_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model.aggro_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.

>>>>

```
#### Re-analysis After Exclusions
There were `r e2.n.bad.subjects.aggro` participants whose calibration score was under 50%. When those participants were removed from the analyses, critical results were the same: there remains a clear gaze bias in the free-viewing condition (first: _b_ =  `r E2_gaze_model.aggro_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model.aggro_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model.aggro_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.
